Binocular combination in the autonomic nervous system

### 2024-08-05 manuscript.tex
Added back line numbers

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Binocular combination in the autonomic nervous system},
  colorlinks=true,
  linkcolor=black,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=Blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{caption} \usepackage{setspace}\doublespacing
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

Number of words for abstract: 199

Number of words for introduction: 896

Number of words for discussion: 600

@@

The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2015}{2015}). The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2008}{2008}, \protect\hyperlink{ref-McDougal2015}{2015}; Wang and Munoz, \protect\hyperlink{ref-Wang2015}{2015}). Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye; Wyatt and Musselman, \protect\hyperlink{ref-Wyatt1981}{1981}). The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception. Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex. Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.

Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (Dacey et al., \protect\hyperlink{ref-Dacey2005}{2005}; Barrionuevo et al., \protect\hyperlink{ref-Barrionuevo2014}{2014}, \protect\hyperlink{ref-Barrionuevo2018}{2018}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}; Spitschan and Cajochen, \protect\hyperlink{ref-Spitschan2019}{2019}). The cones have been shown to drive the initial rapid constriction of the pupils (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (Markwell et al., \protect\hyperlink{ref-Markwell2010}{2010}; McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}). The ipRGCs are a unique photoreceptor class that has been discovered recently (Provencio et al., \protect\hyperlink{ref-Provencio2000}{2000}). They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (Provencio et al., \protect\hyperlink{ref-Provencio2000}{2000}; Panda et al., \protect\hyperlink{ref-Panda2002}{2002}; Ruby et al., \protect\hyperlink{ref-Ruby2002}{2002}), forming a major input to the PON (Dacey et al., \protect\hyperlink{ref-Dacey2003}{2003}). The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by Lucas et al. (\protect\hyperlink{ref-Lucas2003}{2003}), resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction. This same behaviour was later also observed in primates and humans (Gamlin et al., \protect\hyperlink{ref-Gamlin2007}{2007}), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.

A technique known as silent substitution (Estévez and Spekreijse, \protect\hyperlink{ref-Estevez1982}{1982}) can be used to selectively stimulate specific photoreceptor classes. Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others. Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (Shapiro et al., \protect\hyperlink{ref-Shapiro1996}{1996}; Spitschan and Woelders, \protect\hyperlink{ref-Spitschan2018}{2018}, this paper also offers a clear explanation of how to implement silent substitution). Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated. For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Cao et al., \protect\hyperlink{ref-Cao2015}{2015}). Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}), perhaps due to activity in the L-M opponent pathway.

Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (Hubel and Wiesel, \protect\hyperlink{ref-Hubel1962}{1962}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}). For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye (Campbell and Green, \protect\hyperlink{ref-Campbell1965}{1965}; Legge, \protect\hyperlink{ref-Legge1984}{1984}; Baker et al., \protect\hyperlink{ref-Baker2018}{2018}). At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (Ding and Sperling, \protect\hyperlink{ref-Ding2006}{2006}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}; Baker et al., \protect\hyperlink{ref-Baker2007}{2007}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}). This is thought to be due to a process of interocular suppression that compensates for the additional excitatory drive caused by stimulating two eyes. Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.

Most studies that use silent substitution to investigate the PLR stimulate only one eye. If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (e.g.~McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}). While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways. Here we take a different approach, using a custom binocular multiprimary system (see Figure \ref{fig:spectraplots}a,b) that can modulate each (undilated) eye independently, and a binocular eye tracker to measure the diameter of both pupils. We measure the amplitude of pupil modulation (using Fourier analysis) in response to sinusoidal stimulation at 0.5Hz, for stimuli directed at the luminance pathway, L-M cone pathway, S-cone pathway, and melanopsin pathway (see Figure \ref{fig:spectraplots}e-l). Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the two eyes are stimulated at different frequencies (0.5 and 0.4Hz). The results are interpreted using a contemporary model of binocular vision (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}) implemented within a hierarchical Bayesian framework.

@@

To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised viewing system. The light engines were operated via a Python interface to their REST API (Martin et al., \protect\hyperlink{ref-Martin2022}{2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format. When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses. We calculated silent substitution solutions using the \emph{PySilSub} toolbox (Martin et al., \protect\hyperlink{ref-Martin2023}{2023}), using linear algebra. The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source. We used the Stockman and Sharpe (\protect\hyperlink{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in Martin et al., \protect\hyperlink{ref-Martin2023}{2023}) to calculate \(\alpha\)-opic irradiance.

@@

\leavevmode\hypertarget{ref-Barrionuevo2018}{}%
Barrionuevo PA, McAnany JJ, Zele AJ, Cao D (2018) Non-linearities in the Rod and Cone Photoreceptor Inputs to the Afferent Pupil Light Response. Frontiers in Neurology 9.

\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D (2014) Assessing rod, cone, and melanopsin contributions to human pupil flicker responses. Investigative Ophthalmology \& Visual Science 55:719--727.

@@

\leavevmode\hypertarget{ref-Cao2015}{}%
Cao D, Nicandro N, Barrionuevo PA (2015) A five-primary photostimulator suitable for studying intrinsically photosensitive retinal ganglion cell functions in humans. Journal of Vision 15:27 Available at: \url{https://doi.org/10.1167/15.1.27} {[}Accessed July 18, 2023{]}.

@@

\leavevmode\hypertarget{ref-Dacey2005}{}%
Dacey DM, Liao H-W, Peterson BB, Robinson FR, Smith VC, Pokorny J, Yau K-W, Gamlin PD (2005) Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the LGN. Nature 433:749--754 Available at: \url{https://www.nature.com/articles/nature03387} {[}Accessed July 18, 2023{]}.

@@

\leavevmode\hypertarget{ref-Ding2006}{}%
Ding J, Sperling G (2006) A gain-control theory of binocular combination. Proc Natl Acad Sci U S A 103:1141--1146.

@@

\leavevmode\hypertarget{ref-Legge1984}{}%
Legge GE (1984) Binocular contrast summation--ii. Quadratic summation. Vision Res 24:385--394.

@@

\leavevmode\hypertarget{ref-McDougal2008}{}%
McDougal DH, Gamlin PD (2008) Pupillary control pathways. In: The senses: A comprehensive reference, pp 521--536. Elsevier.

@@

\leavevmode\hypertarget{ref-Wang2015}{}%
Wang C-A, Munoz DP (2015) A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. Curr Opin Neurobiol 33:134--140.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Binocular combination in the autonomic nervous system},
  colorlinks=true,
  linkcolor=black,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=Blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{caption} \usepackage{setspace}\doublespacing \usepackage{lineno} \linenumbers
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

Number of words for abstract: 187/250

Number of words for introduction: 634/650

Number of words for discussion: 600/1500

@@

The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2015}{2015}). The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2015}{2015}). Evidence of a binocular component to the PLR is shown by the consensual response of the pupil (stimulation of one eye will cause constriction of the other eye; Wyatt and Musselman, \protect\hyperlink{ref-Wyatt1981}{1981}). The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception. Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex. Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.

Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (e.g.~McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}). Cones drive the initial rapid constriction of the pupils (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}), while the slower and longer activation of the ipRGCs maintains constriction over a prolonged period of time and regulates the post-illumination pupillary response (Markwell et al., \protect\hyperlink{ref-Markwell2010}{2010}; McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}). The ipRGCs are a recently discovered photoreceptor class (Provencio et al., \protect\hyperlink{ref-Provencio2000}{2000}) that express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (Panda et al., \protect\hyperlink{ref-Panda2002}{2002}; Ruby et al., \protect\hyperlink{ref-Ruby2002}{2002}), forming a major input to the PON (Dacey et al., \protect\hyperlink{ref-Dacey2003}{2003}). The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by Lucas et al. (\protect\hyperlink{ref-Lucas2003}{2003}), resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction. Similar behaviour was later observed in primates and humans (Gamlin et al., \protect\hyperlink{ref-Gamlin2007}{2007}) using silent substitution (see Methods), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.

Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (Hubel and Wiesel, \protect\hyperlink{ref-Hubel1962}{1962}). For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye (Campbell and Green, \protect\hyperlink{ref-Campbell1965}{1965}; Baker et al., \protect\hyperlink{ref-Baker2018}{2018}). At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}). This is explained by a process of interocular suppression that cancels out the additional excitatory drive caused by stimulating two eyes. Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway. Here we measure the amplitude of pupil modulations in response to flickering stimuli directed at the luminance, L-M cone, S-cone, and melanopsin pathways (see Figure \ref{fig:spectraplots}e-l). Our key comparisons are between monocular and binocular stimulation, and in a dichoptic masking condition where the two eyes are stimulated at different frequencies. The results are interpreted using a contemporary model of binocular vision (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}) implemented within a hierarchical Bayesian framework.

@@

To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system. The light engines were operated via a Python interface to their REST API (Martin et al., \protect\hyperlink{ref-Martin2022}{2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format. When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses. We used the silent substitution technique (Estévez and Spekreijse, \protect\hyperlink{ref-Estevez1982}{1982}) to selectively stimulate specific photoreceptor classes. Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others. Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (Shapiro et al., \protect\hyperlink{ref-Shapiro1996}{1996}; Spitschan and Woelders, \protect\hyperlink{ref-Spitschan2018}{2018}, this paper also offers a clear explanation of how to implement silent substitution). We calculated silent substitution solutions using the \emph{PySilSub} toolbox (Martin et al., \protect\hyperlink{ref-Martin2023}{2023}), using linear algebra. The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source. We used the Stockman and Sharpe (\protect\hyperlink{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in Martin et al., \protect\hyperlink{ref-Martin2023}{2023}) to calculate \(\alpha\)-opic irradiance.

@@

@@

@@

@@

@@

@@

@@
